Comparison among doublet predictions on benchmarking datasets

### 2024-06-17 analyses/doublet-detection/exploratory-notebooks/03_compare-benchmark-results.Rmd
WIP: Updating PCAs

```{r}
plot_pca_calls <- function(df, 
                           color_column, 
                           pred_column,
                           color_lab) {
  # Plot PCs colored by singlet/doublet, showing doublets on top
  # df is expected to contain columns PC1, PC2, `color_column`, and `pred_column`. These should _not_ be provided as strings
  ggplot(df) + 
    aes(x = PC1, 
        y = PC2, 
        color = {{color_column}}) +
  geom_point(
    size = 0.75, 
    alpha = 0.6
  ) +
  scale_color_manual(name = color_lab, values = c("black", "lightblue")) + 
  geom_point(
    data = dplyr::filter(df, {{color_column}} == "doublet"), 
    color = "black",
    size = 0.75
  ) +
  theme(
    legend.title.position = "top",
    legend.position = "bottom"
  )
}

@@

@@

      # First, ground truth
      p1 <- plot_pca_calls(
        df, 
        color_column = ground_truth, 
        color_lab = "Ground truth"
      )

      # Second, consensus call
      p2 <- plot_pca_calls(
        df, 
        color_column = consensus_call, 
        color_lab = "Consensus call"
      )

      # Third, call type
      p3 <- plot_pca_metrics(
        df,
        call_type, 
        metric_colors = confusion_colors
      )

      # combine and plot
      plot( p1 + p2 + p3 + plot_annotation(glue::glue("PCA for {dataset}")) + plot_layout(ncol=4, widths = c(1,1,1)) )
    }
  )
```

>>>>

```{r}
plot_pca_calls <- function(df, 
                           color_column, 
                           pred_column,
                           title) {
  # Plot PCs colored by singlet/doublet, showing doublets on top
  # df is expected to contain columns PC1, PC2, `color_column`, and `pred_column`. These should _not_ be provided as strings
  ggplot(df) + 
    aes(x = PC1, 
        y = PC2, 
        color = {{color_column}}) +
  geom_point(
    size = 0.75, 
    alpha = 0.6
  ) +
  scale_color_manual(name = "", values = c("black", "gray80")) + 
  geom_point(
    data = dplyr::filter(df, {{color_column}} == "doublet"), 
    color = "black",
    size = 0.75
  ) +
  ggtitle(title) +
  theme(
    legend.title.position = "top",
    legend.position = "bottom"
  )
}

@@

MORE MORE MORE MORE MORE FILL IN THIS TEXT!!!

@@

      # Top row: methods themselves ---
      p1 <- plot_pca_calls(
        df, 
        color_column = scdbl_prediction, 
        title = "scDblFinder prediction"
      )

      p2 <- plot_pca_calls(
        df, 
        color_column = scrublet_prediction, 
        title = "scrublet prediction"
      )

      p3 <- plot_pca_calls(
        df, 
        color_column = cxds_prediction, 
        color_lab = "cxds prediction"
      )

      # Bottom row: consensus  --
      p4 <- plot_pca_calls(
        df, 
        color_column = ground_truth, 
        title = "Ground truth"
      )

      # Second, consensus call
      p5 <- plot_pca_calls(
        df, 
        color_column = consensus_call, 
        title = "Consensus call"
      )

      # Third, call type
      p6 <- plot_pca_metrics(
        df,
        call_type, 
        metric_colors = confusion_colors
      )

      # combine and plot
      plot( 
        (p1 + p2 + p3) / (p4 + p5 + p6) + 
          plot_annotation(glue::glue("PCA for {dataset}")) + 
          plot_layout(guides = "collect"))
    }
  )
```
